### 2020-08-03 paper/main.tex

>>>>

\subsubsection{Amenable holes.}

For a shortest odd hole $C$ in $G$, we will call a node $v \in V(G) \setminus V(C)$ $C$-\emph{major} iff the set of its neighbors in C is not contained in any 3-node path of $C$. An odd hole $C$ will be called \emph{clean} if no vertex is $C$-major.

A hole $C$ of $G$ is \emph{amenable} iff C is a shortest odd hole in $G$ of length at least 7, and for every anticonnected set $X$ of $C$-major nodes, there is an $X$-complete edge in $C$ (an edge is $X$-complete iff both its ends are $X$-complete).

The rest of the algorithm rests upon the following theorem:

\begin{theorem}
	Let $G$ be a graph, such that $G$ and $\overline{G}$ contain no Pyramid, no Jewel and no configuration of types $\T_1, \T_2$ or $\T_3$. Then every shortest hole in $G$ is amenable.
	\TODO{Any ideas on what else to say here? List all 9 steps?}
\end{theorem}

For a shortest odd hole $C$ in $G$, a subset $X$ of $V(G)$ is a \emph{near-cleaner for $C$} iff $X$ contains all $C$-major nodes and $X \cap V(C)$ is a subset of node set of some 3-node path of $C$.
